\documentclass[a4paper,11pt,pdf]{pacmanreport}

%%=== Aditional packages


%%=== Local definitions

%% ================================
%% PROJECT INFO 

\project{}
\projectid{FP7-IST-60918}
\projectstart{1 March 2013}
\duration{36}

%% ================================
%% MILESTONE INFO 

\title{Grasping of unfamiliar objects with compositional models}
\deliverableid{Milestone 4.3}
\author{M. Kopicki, ...}
\address{University of Birmingham}
\email{M.S.Kopicki@cs.bham.ac.uk}
\headertitle{shorted title}
\headerauthor{shortauthor}

\duedate{2015-02-27}
\submissiondate{2015-02-27}
\leadpartner{UBHAM}
\revision{draft}
\disseminationlevel{PU}


%% UNCOMMENT: to get the logo; if you've copied this file to a directory yearX/wpY/ then this should work
\reportlogo{pacmanlogo}





\begin{document}

\maketitle

\begin{abstract}
\noindent Here comes the abstract
\end{abstract}


\vspace{.2em}
\hrule

\vspace{.2em}
\footnotesize

\tableofcontents

\normalsize

\newpage

\section{Milestone Summary and Context}

What was the milestone that you are examining? What were the criteria for achieving it? What role does achievement of the milestone play in the whole project\cite{ProjectWebsite}? How will its achievement as presented in this report contribute to the PaCMan scenarios and prototypes? 


\newpage

\section{Report on Milestone Achievement}

How have the tasks been addressed? To what extent have the intended objectives been achieved? Why, how -- or why not? In particular what concrete acceptance tests, or experimental results show that the milestone has been achieved.

\newpage
\bibliographystyle{IEEEtran}
\bibliography{../shared_bibliography/abbreviations,bibliography/MS43}

\newpage
\appendix
\section{Annexes}

Here you should briefly describe the papers attached that provide evidence for achievement of the milestone. Mention titles, authors, publication info; abstract; and a one-liner relating the publication back to the discussion on actual work performed. 









\end{document}
